---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS_2014_haven.R")
source("makeTables.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between gun ownership and race, sex, political views, opinions on capitol punishment and belief in god. The data is from the 2014 general social survey.



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
barchartGC(race_table,type="percent" , main= "Race vs. Gun Ownership")
```
After viewing this data graphically, it appears that WHITE, BLACK, and OTHER all voted “no” on gun ownership. This means that people should not own guns themselves

```{r}
barchartGC(sex_table,type="percent" , main= "Sex vs. Gun Ownership")
```
In this dataset, the comparison we can determine is that both males and females say “no” to gun ownership.

```{r}
barchartGC(polviews_table,type="percent" , main= "Political Beliefs vs. Gun Ownership")
```
In this dataset we are still seeing a lot of “no” between the groups.

```{r}
barchartGC(cappun_table,type="percent" , main= "Capital Punishment vs. Gun Ownership")
```
ALthough in this dataset, the idea of no ownership of guns stands strong especially with those that believe in capital punishment.

```{r}
barchartGC(god_table,type="percent", main= "Belief in God vs. Gun Ownership")
```
The relationship that we can see here is that it is completely even between all of the groups, saying “yes” or “no”.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

# Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
